---
title: "IMM reliability"
author: "Attila Szuts"
date: '2020 április 9 '
output:
  html_document:
    toc: true
    theme: united
    number_sections: true
editor_options: 
  chunk_output_type: console
---

# Data processing 

## Data input and opening libraries

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(readr)
library(tidyverse)
library(readxl)
library(lubridate)
library(ggplot2)
library(stringr)
library(vroom)
library(janitor)
library(widyr)
# library(data.table)
library(ggpubr)
library(vroom)
library(lubridate)
library(corrr)
library(multicon)
library(VGAM)
library(ggcorrplot)
library(broom)
library(lmerTest)
library(lme4)
library(dotwhisker)
```

## Explicit

### Importing data

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
explicit_raw <-
  bind_rows(
    read_csv("data/Round 1/data.csv") %>% mutate(measurement = 1),
    read_csv("data/Round 2/data.csv") %>% mutate(measurement = 2)
  ) 
```

### Reversing items, creating groups, creating means of explicit measures

```{r}
explicit <- 
  explicit_raw %>% 
  tidyr::extract(col = participant, 
          into = c(NA, "id", NA), 
          regex = "^(.*s.)(.*)(.txt)$") %>% 
  clean_names() %>% 
  drop_na(time_end) %>% 
  mutate(neptun_1 = str_to_lower(neptun_1)) %>% 
  mutate_at(c("time_start", "time_end"), ymd_hm) %>% 
  mutate_at(c("time_start", "time_end"), as_date) %>% 
  group_by(measurement) %>% 
  distinct(neptun_1, .keep_all = TRUE) %>% 
  ungroup() %>% 
#creating 2-week and 4-week group, filtering participants that were only in one part  
  group_by(neptun_1) %>% 
  arrange(neptun_1, time_end) %>% 
  mutate(time_end_lag = time_end - dplyr::lag(time_end),
         time_end_lead = dplyr::lead(time_end)- time_end,
         time_end_lag = replace_na(time_end_lag, 0),
         time_end_lead = replace_na(time_end_lead, 0),
         time_end_diff = time_end_lag + time_end_lead) %>% 
  filter(time_end_diff > 0) %>% 
  mutate(group = ifelse(time_end_diff > 20, 1, 0)) %>% 
  select(-c(time_end_lag, time_end_lead, time_end)) %>% 
  ungroup() %>% 
#reversing items
  mutate_at(vars(iq1_1, iq2_1, fms3_1, fms4_1, cr_ms3_1, cr_ms4_1, ch_ms3_1, ch_ms4_1), 
            ~recode(., `1` = 6,
                    `2` = 5,
                    `3` = 4,
                    `4` = 3,
                    `5` = 2,
                    `6` = 1,
            )) %>% 
  mutate_at(vars(failurescenario_1, criticismscenario_1), 
            ~recode(., `1` = 5,
                    `2` = 4,
                    `4` = 2,
                    `5` = 1,
            )) %>% 
#creating means of explicit measures
  mutate(iqms_avg = rowMeans(x = select(.data = ., starts_with(match = "iq")))) %>% 
  mutate(crms_avg = rowMeans(x = select(.data = ., starts_with(match = "cr_ms")))) %>% 
  mutate(chms_avg = rowMeans(x = select(.data = ., starts_with(match = "ch_ms")))) %>% 
  mutate(fms_avg = rowMeans(x = select(.data = ., starts_with(match = "fms")))) %>% 
  mutate(fsc_avg = rowMeans(x = select(.data = ., starts_with(match = "failure")))) %>% 
  mutate(crsc_avg = rowMeans(x = select(.data = ., starts_with(match = "criticism")))) %>% 
  dplyr::select(neptun_1, id, gender_1, age_1, iqms_avg, crms_avg, chms_avg, fms_avg, fsc_avg, crsc_avg, challengescenario_1, measurement, group, time_end_diff)
```

Neptun codes that were removed from second round
```{r}
excluded <- setdiff(explicit_raw %>% filter(measurement == 2) %>% mutate(neptun_1 = tolower(`Neptun:1`)) %$% neptun_1,
                    explicit %>% filter(measurement == 2) %$% neptun_1)
#participant ids that were removed from explicit because they didn't complete second round
excluded_id <- explicit_raw %>% filter(`Neptun:1` %in% excluded) %$% participant
```

Counting number of participants in groups
The 2 week group is coded as group 0, the 4 week group is coded as group 1.
```{r}
explicit %>% 
  count(group)
```

Plotting frequency of number of days between data collections
```{r}
ggplot(explicit, aes(time_end_diff)) +
  geom_bar() + 
  xlab('Days between measures') + 
  ylab('Number of particpants') + 
  theme_classic()
```

## Implicit

### Importing data
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
#defining path
files1 <- list.files(path = "D:/Documents/Egyebek/Thesis/data/Round 1", pattern = "immtest.*.txt$", full.names = TRUE)
files2 <- list.files(path = "D:/Documents/Egyebek/Thesis/data/Round 2", pattern = "immtest.*.txt$", full.names = TRUE)

#importing data files
gnat_raw <- 
  bind_rows(
  vroom::vroom(file = files1, 
        id = "id", 
        col_names = c("block", "block_id", "word", "max_rt", "trial_type", "word_category", "rt", "error", "target")) %>% mutate(measurement = 1),
  vroom::vroom(file = files2, 
        id = "id", 
        col_names = c("block", "block_id", "word", "max_rt", "trial_type", "word_category", "rt", "error", "target")) %>% mutate(measurement = 2)) %>% 
  tidyr::extract(col = id, 
          into = c(NA, "id", NA), 
          regex = "^(.*data.)(.*)(.txt)$")
```
### Filtering observations based on error rate 

Criteria: 

* Block error rate below 60%
* Overall error rate below 80%
* Erroneous association
* Response latency under 300 ms
* Response latency above 1399 ms

filtering observations and creating d-scores
```{r}
#important targets
important_targets <- c("chall_pos", "chall_neg", "crit_pos", "crit_neg")

implicit <- 
  gnat_raw %>% 
  #filter only important trials and only go_trials 
  filter(target %in%important_targets,
         trial_type == 'go_trial') %>% 
  #filtering out participants that didnt complete the second round
  filter(!id %in% excluded_id) %>%
  #checking for block error rate per participant
  group_by(id, target) %>% 
  mutate(correct_block = 1 - mean(error)) %>% 
  ungroup() %>% 
  # checking for overall error rate per participant
  group_by(id) %>% 
  mutate(correct_all = 1 - mean(error)) %>% 
  ungroup() %>% 
  # filter overall and block error rates, filter too quick and too slow responses
  filter(correct_block > 0.6 & correct_all > 0.8 & error == 0,
         rt > 300 & rt < 1399) %>%
  #calculating d-scores
  group_by(measurement, id) %>% 
  mutate(pers_sd = sd(rt)) %>% 
  ungroup() %>% 
  group_by(measurement, id, target, pers_sd) %>% 
  summarise(rt = mean(rt)) %>% 
  mutate(d = rt/pers_sd) %>% 
  ungroup() %>% 
  select(-pers_sd) %>%
  tidyr::pivot_wider(id_cols = c(id, measurement), names_from = target, values_from = c(d, rt), names_glue = "{target}_{.value}") %>% 
  mutate(challenge_rt = chall_neg_rt - chall_pos_rt,
         crit_rt = crit_neg_rt - crit_pos_rt,
         challenge_d = chall_neg_d - chall_pos_d,
         crit_d = crit_neg_d - crit_pos_d) 
```


Words RT
```{r}
words <- gnat_raw %>% 
  #filter only important trials and only go_trials 
  filter(target %in%important_targets,
         trial_type == 'go_trial') %>% 
  #filtering out participants that didnt complete the second round
  filter(!id %in% excluded_id) %>%
  #checking for block error rate per participant
  group_by(id, target) %>% 
  mutate(correct_block = 1 - mean(error)) %>% 
  ungroup() %>% 
  # checking for overall error rate per participant
  group_by(id) %>% 
  mutate(correct_all = 1 - mean(error)) %>% 
  ungroup() %>% 
  # filter overall and block error rates, filter too quick and too slow responses
  filter(correct_block > 0.6 & correct_all > 0.8 & error == 0,
         rt > 300 & rt < 1399) %>%
  group_by(measurement, word_category, word) %>% 
  summarise(mean_rt = mean(rt),
            median_rt = median(rt),
            range_rt = max(rt)-min(rt),
            min_rt = min(rt),
            max_rt = max(rt),
            IQR_rt = IQR(rt)) %>%
  pivot_wider(id_cols = word, names_from = measurement, values_from = c(2, 4)) %>% 
  rename(word_category = "word_category_1") %>% 
  select(-word_category_2)
```

## Unite implicit with explicit

Excluded participants from final that had too high error rate in implicit task
```{r}
final <- left_join(explicit, implicit, by = c("id", "measurement")) %>% 
  filter(neptun_1 != "q69vn2",
         neptun_1 != "bm0vx1") %>% 
  pivot_wider(id_cols = c(neptun_1, gender_1, age_1, group, time_end_diff), names_from = measurement, values_from = c(3:10, 13, 15:26)) %>% 
  mutate(gender = gender_1_1, 
         age = age_1_1,
         group = group_1,
         time_end_diff_1 = time_end_diff) %>% 
  select(-c(gender_1_1, gender_1_2, age_1_1, age_1_2, group_1, group_2, time_end_diff)) %>% 
  rename(time_end_diff = "time_end_diff_1")
```

Long format for plots
```{r}
final_long <- final %>% 
  select(c(1, 14:37, 40, 41)) %>% 
  rename(chall_score_rt_1 = "challenge_rt_1",
         chall_score_rt_2 = "challenge_rt_2",
         crit_score_rt_1 = "crit_rt_1",
         crit_score_rt_2 = "crit_rt_2",
         chall_score_d_1 = "challenge_d_1",
         chall_score_d_2 = "challenge_d_2",
         crit_score_d_1 = "crit_d_1",
         crit_score_d_2 = "crit_d_2",
         days = "time_end_diff",
         id = "neptun_1") %>% 
  pivot_longer(cols = c(2:25), ) %>% 
  separate(name, c("block_1", "block_2", "measurement_type", "measurement_round")) %>% 
  unite(col = "block", c("block_1", "block_2"), sep = "_") %>% 
  mutate(
    days = ifelse(measurement_round == 2, days, 0)
  )
```

Long format for glm
```{r}
final_day_diff <- final %>% 
  select(c(1, 14:37, 40, 41)) %>% 
  rename(chall_score_rt_1 = "challenge_rt_1",
         chall_score_rt_2 = "challenge_rt_2",
         crit_score_rt_1 = "crit_rt_1",
         crit_score_rt_2 = "crit_rt_2",
         chall_score_d_1 = "challenge_d_1",
         chall_score_d_2 = "challenge_d_2",
         crit_score_d_1 = "crit_d_1",
         crit_score_d_2 = "crit_d_2",
         days = "time_end_diff",
         id = "neptun_1") %>% 
  pivot_longer(cols = c(2:25), ) %>%
  separate(name, c("block_1", "block_2", "measurement_type", "measurement_round")) %>% 
  unite(col = "block", c("block_1", "block_2"), sep = "_") %>% 
  pivot_wider(id_cols = c(id, measurement_round, days, group), names_from = c(block, measurement_type), values_from = value) %>% 
  mutate(
    days = ifelse(measurement_round == 2, days, 0)
  )
```


# Analysis

* D-score difference between measures
* words RT correlation between measures
* test-retest reliability
* difference of effect size between groups

## Assumption checks

Normality test
```{r}
final %>% 
  select(c(14:37)) %>% 
  map(shapiro.test)
```

Normality test for t-test
```{r}
shapiro.test(final$challenge_d_1 - final$challenge_d_2)
shapiro.test(final$challenge_rt_1 - final$challenge_rt_2)
shapiro.test(final$crit_d_1 - final$crit_d_2)
shapiro.test(final$crit_rt_1 - final$crit_rt_2)
```

word rt normality test
```{r}
# normal
shapiro.test(words$mean_rt_1)
shapiro.test(words$mean_rt_2)

words %>% 
  filter(word_category == "challenge") %>% 
  select(mean_rt_1, mean_rt_2) %>% 
  map(shapiro.test)

words %>% 
  filter(word_category == "criticism") %>% 
  select(mean_rt_1, mean_rt_2) %>% 
  map(shapiro.test)

words %>% 
  filter(word_category == "positive") %>% 
  select(mean_rt_1, mean_rt_2) %>% 
  map(shapiro.test)

words %>% 
  filter(word_category == "criticism") %>% 
  select(mean_rt_1, mean_rt_2) %>% 
  map(shapiro.test)
```

## Descriptives

### Participants

```{r}
# gender 1 -> woman
final %>% 
  summarise(
    mean_age = mean(age),
    sd_age = sd(age)
  )
final %>% 
  count(
    gender
  )
```

### D-score difference t-test

```{r}
final %>% 
  select(c(challenge_d_1, challenge_d_2, challenge_rt_1, challenge_rt_2, crit_d_1, crit_d_2, crit_rt_1,crit_rt_2)) %>% 
  summarise(
    #challenge d-score
    mean_ch_d_1 = mean(challenge_d_1),
    sd_ch_d_1 = sd(challenge_d_1),
    mean_ch_d_2 = mean(challenge_d_2),
    sd_ch_d_2 = sd(challenge_d_2),
    #criticism d-score
    mean_cr_d_1 = mean(crit_d_1),
    sd_cr_d_1 = sd(crit_d_1),
    mean_cr_d_2 = mean(crit_d_1),
    sd_cr_d_2 = sd(crit_d_2),
    #challenge rt
    mean_ch_rt_1 = mean(challenge_rt_1),
    sd_ch_rt_1 = sd(challenge_rt_1),
    mean_ch_rt_2 = mean(challenge_rt_2),
    sd_ch_rt_2 = sd(challenge_rt_2),
    #criticism rt
    mean_cr_rt_1 = mean(crit_rt_1),
    sd_cr_rt_1 = sd(crit_rt_1),
    mean_cr_rt_2 = mean(crit_rt_1),
    sd_cr_rt_2 = sd(crit_rt_2)
  ) %>% 
  view()
```

### Test retest reliability

```{r}
final_long %>% 
  group_by(measurement_type, measurement_round, block) %>% 
  summarise(
    mean = mean(value),
    sd = sd(value)
  ) %>% 
  pivot_wider(id_cols = c(block, measurement_round), values_from = c(mean, sd), names_from = c(measurement_type)) %>% 
  select(c(1:3, 5, 4, 6)) %>% 
  #write_csv("D:/Documents/Egyebek/Thesis/data/Temp/descriptives.csv")
  view()
```
### Effect of days

boxplot for d-scores
```{r}
final_long %>% 
  mutate(measurement_round = ifelse(measurement_round == 1, "first", "second")) %>% 
  filter(measurement_type == "d") %>% 
  ggplot(aes(block, value, fill = measurement_round)) + 
  geom_boxplot(position = "dodge") + 
  scale_fill_manual("Measurement round", values=c("lightgreen", "darkgreen")) +
  xlab("Target blocks") +
  ylab("D-scores") +
  labs(title = "Boxplot of d-scores by trial blocks and measurement rounds separately") +
  theme_classic()
```

boxplot for rt
```{r}
final_long %>% 
  mutate(measurement_round = ifelse(measurement_round == 1, "first", "second")) %>% 
  filter(measurement_type == "rt") %>% 
  ggplot(aes(block, value, fill = measurement_round)) + 
  geom_boxplot(position = "dodge") + 
  scale_fill_manual("Measurement round", values=c("lightgreen", "darkgreen")) +
  xlab("Target blocks") +
  ylab("RT(ms)") +
  labs(title = "Boxplot of Reaction Times (RT) by trial blocks and measurement rounds separately") +
  theme_classic()
```
### Words

```{r}
words %>% 
  group_by(word_category) %>% 
  summarise(
    mean_1 = mean(mean_rt_1),
    SD_1 = sd(mean_rt_1),
    mean_2 = mean(mean_rt_2),
    SD_2 = sd(mean_rt_2)) %>% 
  view()

words %>% 
  summarise(
    mean_1 = mean(mean_rt_1),
    SD_1 = sd(mean_rt_1),
    mean_2 = mean(mean_rt_2),
    SD_2 = sd(mean_rt_2)) %>% 
  view()
```
## Hypothesis testing

### D-score difference between measures for challenge and criticism
```{r}
# t test
t.ch_d <- t.test(final$challenge_d_1, final$challenge_d_2, paired = T)
t.ch_rt <- t.test(final$challenge_rt_1, final$challenge_rt_2, paired = T)
t.cr_d <- t.test(final$crit_d_1, final$crit_d_2, paired = T)
t.cr_rt <- t.test(final$crit_rt_1, final$crit_rt_2, paired = T)

t.ch_d
t.ch_rt
t.cr_d
t.cr_rt
```

### Words rt correlation
```{r}
cor.test(words$mean_rt_1, words$mean_rt_2, method = "pearson")

words %>% 
  filter(word_category == "challenge") %$% 
  cor.test(mean_rt_1, mean_rt_2)

words %>% 
  filter(word_category == "criticism") %$% 
  cor.test(mean_rt_1, mean_rt_2)

words %>% 
  filter(word_category == "positive") %$% 
  cor.test(mean_rt_1, mean_rt_2)

words %>% 
  filter(word_category == "negative") %$% 
  cor.test(mean_rt_1, mean_rt_2)
```

### Test-retest reliability

```{r}
cor.test(final$chall_neg_d_1, final$chall_neg_d_2, method = "spearman")
cor.test(final$chall_pos_d_1, final$chall_pos_d_2, method = "spearman")
cor.test(final$crit_neg_d_1, final$crit_neg_d_2, method = "spearman")
cor.test(final$crit_pos_d_1, final$crit_pos_d_2, method = "spearman")
cor.test(final$challenge_d_1, final$challenge_d_2, method = "pearson")
cor.test(final$crit_d_1, final$crit_d_2, method = "spearman")

cor.test(final$chall_neg_rt_1, final$chall_neg_rt_2, method = "spearman")
cor.test(final$chall_pos_rt_1, final$chall_pos_rt_2, method = "spearman")
cor.test(final$crit_neg_rt_1, final$crit_neg_rt_2, method = "spearman")
cor.test(final$crit_pos_rt_1, final$crit_pos_rt_2, method = "spearman")
cor.test(final$challenge_rt_1, final$challenge_rt_2, method = "spearman")
cor.test(final$crit_rt_1, final$crit_rt_2, method = "spearman")
```

### Difference in effect size between groups
```{r}
#d
lmer_ch_n_d <- lmer(chall_neg_d ~ days + (1 | id), data = final_day_diff)
lmer_ch_p_d <- lmer(chall_pos_d ~ days + (1 | id), data = final_day_diff)
lmer_cr_n_d <- lmer(crit_neg_d ~ days + (1 | id), data = final_day_diff)
lmer_cr_p_d <- lmer(crit_pos_d ~ days + (1 | id), data = final_day_diff)
lmer_ch_sc_d <- lmer(chall_score_d ~ days + (1 | id), data = final_day_diff)
lmer_cr_sc_d <- lmer(crit_score_d ~ days + (1 | id), data = final_day_diff)

#rt
lmer_ch_n_rt <- lmer(chall_neg_rt ~ days + (1 | id), data = final_day_diff)
lmer_ch_p_rt <- lmer(chall_pos_rt ~ days + (1 | id), data = final_day_diff)
lmer_cr_n_rt <- lmer(crit_neg_rt ~ days + (1 | id), data = final_day_diff)
lmer_cr_p_rt <- lmer(crit_pos_rt ~ days + (1 | id), data = final_day_diff)
lmer_ch_sc_rt <- lmer(chall_score_rt ~ days + (1 | id), data = final_day_diff)
lmer_cr_sc_rt <- lmer(crit_score_rt ~ days + (1 | id), data = final_day_diff)
```

```{r}
summary(lmer_ch_n_d)
summary(lmer_ch_p_d)
summary(lmer_cr_n_d)
summary(lmer_cr_p_d)
summary(lmer_ch_sc_d)
summary(lmer_cr_sc_d)

summary(lmer_ch_n_rt)
summary(lmer_ch_p_rt)
summary(lmer_cr_n_rt)
summary(lmer_cr_p_rt)
summary(lmer_ch_sc_rt)
summary(lmer_cr_sc_rt)

```

```{r}
confint(lmer_ch_n_d, c("days"))
confint(lmer_ch_p_d, c("days"))
confint(lmer_cr_n_d, c("days"))
confint(lmer_cr_p_d, c("days"))
confint(lmer_ch_sc_d, c("days"))
confint(lmer_cr_sc_d, c("days"))

#rt
confint(lmer_ch_n_rt, c("days"))
confint(lmer_ch_p_rt, c("days"))
confint(lmer_cr_n_rt, c("days"))
confint(lmer_cr_p_rt, c("days"))
confint(lmer_ch_sc_rt, c("days"))
confint(lmer_cr_sc_rt, c("days"))

```


## Plots and figures

### Correlation matrix for implicit results 

d-scores
```{r fig.dim = c(6,6), fig.align = "center", dpi = 400}
results_d <- final %>% 
  select(c(14:21, 34:37)) %>% 
  cor(method = "spearman") %>% 
  round(3)
results_d.p <- cor_pmat(results_d)
ggcorrplot(results_d, 
           outline.color = "white", 
           type = "lower", 
           colors = c("blue", "white", "darkgreen"),
           ggtheme = ggplot2::theme_classic(),
           lab = T,
           p.mat = results_d.p,
           insig = "pch",
           show.legend = F,
           lab_size = 4,
           pch = 0,
           pch.cex = 13,
           title = "fields without outline represent significant correlations")
```

RT
```{r fig.dim = c(6,6), fig.align = "center", dpi = 400}
results_rt <- final %>% 
  select(c(22:33)) %>% 
  cor(method = "spearman") %>% 
  round(3)
results_rt.p <- cor_pmat(results_rt)
ggcorrplot(results_rt, 
           outline.color = "white", 
           type = "lower", 
           colors = c("blue", "white", "darkgreen"),
           ggtheme = ggplot2::theme_classic(),
           lab = T,
           p.mat = results_rt.p,
           insig = "pch",
           show.legend = F,
           lab_size = 4,
           pch = 0,
           pch.cex = 13,
           title = "fields without outline represent significant correlations")
```

### Difference in effect size between groups

Adding predictions
```{r include=FALSE}
pred <- final_long %>% 
  mutate(
    pred = ifelse(final_long$block == "chall_neg" & final_long$measurement_type == "d", predict(lmer_ch_n_d, re.form = NA),
                  ifelse(final_long$block == "chall_pos" & final_long$measurement_type == "d", predict(lmer_ch_p_d, re.form = NA),
                         ifelse(final_long$block == "crit_neg" & final_long$measurement_type == "d", predict(lmer_cr_n_d, re.form = NA),
                                ifelse(final_long$block == "crit_pos" & final_long$measurement_type == "d", predict(lmer_cr_p_d, re.form = NA),
                                       ifelse(final_long$block == "chall_score" & final_long$measurement_type == "d", predict(lmer_ch_sc_d, re.form = NA),
                                              ifelse(final_long$block == "crit_score" & final_long$measurement_type == "d", predict(lmer_cr_sc_d, re.form = NA),
                                                     #rt
                                                     ifelse(final_long$block == "chall_neg" & final_long$measurement_type == "rt", predict(lmer_ch_n_rt, re.form = NA),
                                                            ifelse(final_long$block == "chall_pos" & final_long$measurement_type == "rt", predict(lmer_ch_p_rt, re.form = NA),
                                                                   ifelse(final_long$block == "crit_neg" & final_long$measurement_type == "rt", predict(lmer_cr_n_rt, re.form = NA),
                                                                          ifelse(final_long$block == "crit_pos" & final_long$measurement_type == "rt", predict(lmer_cr_p_rt, re.form = NA),
                                                                                 ifelse(final_long$block == "chall_score" & final_long$measurement_type == "rt", predict(lmer_ch_sc_rt, re.form = NA), predict(lmer_cr_sc_rt, re.form = NA)))))))))))),
    pred1 = ifelse(final_long$block == "chall_neg" & final_long$measurement_type == "d", predict(lmer_ch_n_d),
                  ifelse(final_long$block == "chall_pos" & final_long$measurement_type == "d", predict(lmer_ch_p_d),
                         ifelse(final_long$block == "crit_neg" & final_long$measurement_type == "d", predict(lmer_cr_n_d),
                                ifelse(final_long$block == "crit_pos" & final_long$measurement_type == "d", predict(lmer_cr_p_d),
                                       ifelse(final_long$block == "chall_score" & final_long$measurement_type == "d", predict(lmer_ch_sc_d),
                                              ifelse(final_long$block == "crit_score" & final_long$measurement_type == "d", predict(lmer_cr_sc_d),
                                                     #rt
                                                     ifelse(final_long$block == "chall_neg" & final_long$measurement_type == "rt", predict(lmer_ch_n_rt),
                                                            ifelse(final_long$block == "chall_pos" & final_long$measurement_type == "rt", predict(lmer_ch_p_rt),
                                                                   ifelse(final_long$block == "crit_neg" & final_long$measurement_type == "rt", predict(lmer_cr_n_rt),
                                                                          ifelse(final_long$block == "crit_pos" & final_long$measurement_type == "rt", predict(lmer_cr_p_rt),
                                                                                 ifelse(final_long$block == "chall_score" & final_long$measurement_type == "rt", predict(lmer_ch_sc_rt, re.form = NA), predict(lmer_cr_sc_rt))))))))))))
    
  )
```

Difference in d-scores
```{r fig.align = "center"}
pred %>% 
  mutate(
    measurement_round = ifelse(measurement_round == 1, "first", "second"),
    group = as.factor(ifelse(group == 0, "2-week", "4-week"))
  ) %>% 
  filter(measurement_type == "d") %>% 
  ggplot(aes(days, value, color = group)) +
  geom_point(alpha = 0.3) + 
  geom_line(aes(group = id), alpha = 0.3) +
  facet_grid(cols = vars(block)) +
  # individual prediction of changes
  #geom_line(colour = "red", aes(y=pred1, group = id), alpha = 1) +
  geom_line(colour = "red", aes(y=pred, group=id)) +
  scale_color_manual("Groups", values=c("darkgreen", "blue")) +
  xlab("Days between measures") + 
  ylab("D-score") + 
  labs( 
    title = "D-score difference between measures",
    subtitle = "Does the number of days between measures have an effect on the difference between d-scores?") +
  theme_classic() 
```

Difference in reaction times
```{r fig.align = "center"}
pred %>% 
  mutate(
    measurement_round = ifelse(measurement_round == 1, "first", "second"),
    group = as.factor(ifelse(group == 0, "2-week", "4-week"))
  ) %>% 
  filter(measurement_type == "rt") %>% 
  ggplot(aes(days, value, color = group)) +
  geom_point(alpha = 0.3) + 
  geom_line(aes(group = id), alpha = 0.3) +
  facet_grid(cols = vars(block)) +
  # individual prediction of changes
  #geom_line(colour = "red", aes(y=pred1, group = id), alpha = 1) +
  geom_line(colour = "red", aes(y=pred, group=id)) +
  scale_color_manual("Groups", values=c("darkgreen", "blue")) +
  xlab("Days between measures") + 
  ylab("RT(ms)") + 
  labs( 
    title = "Reaction Time (RT) difference between measures",
    subtitle = "Does the number of days between measures have an effect on the difference between reaction times?") +
  theme_classic() 
```

