---
title: "IMM reliability"
author: "Attila"
date: '2020 április 9 '
output: html_document
editor_options: 
  chunk_output_type: console
---

#Data input and opening libraries
```{r}
library(readr); library(tidyverse); library(readxl); library(lubridate); library(ggplot2); library(stringr)
setwd("D:/Documents/Dropbox/Implicit Mindset Measure")
round1 <- read_csv("D:/Documents/Dropbox/Implicit Mindset Measure/Data/Source/Round 1/data.csv")
round2 <- read_csv("D:/Documents/Dropbox/Implicit Mindset Measure/Data/Source/Round 2/data.csv")
```

##Responses that have not been completed
Extracting responses based on missing completion time ('TIME_end')
```{r}
missing1 <- round1[is.na(round1$TIME_end),]
missing2 <- round2[is.na(round2$TIME_end),]
```

##Preparing data to be united
Cleaning variable names, and dropping missing cases. Changing Neptun codes to upper case. Filtering out duplicate answers.
```{r}
time1 <- round1 %>% 
  select(c("participant", "Neptun:1", "TIME_start", "TIME_end")) %>% 
  rename(TIME_start_first = "TIME_start", TIME_end_first = "TIME_end", participant_first = "participant") %>% 
  drop_na()
time2 <- round2 %>% 
  select(c("participant", "Neptun:1", "TIME_start", "TIME_end")) %>% 
  rename(TIME_start_second = "TIME_start", TIME_end_second = "TIME_end", participant_second = "participant") %>% 
  drop_na()

#neptun codes to upper case
time1$`Neptun:1` <- toupper(time1$`Neptun:1`)
time2$`Neptun:1` <- toupper(time2$`Neptun:1`)

#neptun codes more than once in data
neptun_duplicate_time1 <- time1 %>% 
  count(`Neptun:1`) %>% 
  filter(n > 1)
neptun_duplicate_time2 <- time2 %>% 
  count(`Neptun:1`) %>% 
  filter(n > 1)
```

#Creating groups
The 2 week group is coded as group 0, the 4 week group is coded as group 1.
##Joining separate rounds
Cases missing first round means, they either did not complete round 1 or they made a typo in their Neptun code and therefore it can't be automatically matched to it.
```{r}
joined <- left_join(time2, time1, by = "Neptun:1")
missing_joined_first_round <- joined[is.na(joined$TIME_end_first),]
#number of times Neptun codes appear
neptun_duplicate_joined <- joined %>% 
  count(`Neptun:1`) %>% 
  filter(n > 1)
```

##Converting to date
```{r}
joined$TIME_end_first <- as.Date(joined$TIME_end_first)
joined$TIME_end_second <- as.Date(joined$TIME_end_second)
joined$TIME_start_first <- as.Date(joined$TIME_start_first)
joined$TIME_start_second <- as.Date(joined$TIME_start_second)
```

##Adding days between data collection column and filtering missing values
```{r}
joined <- joined %>% 
  mutate(
    TIME_between_end = TIME_end_second - TIME_end_first
  ) 
missing_joined_TIME_between <- joined %>% 
  dplyr::filter(is.na("TIME_end_between"))
joined <- joined %>% 
  drop_na(TIME_between_end)
```

## Exporting missing values and checking manually
```{r}
#write_csv2(neptun_duplicate_joined, "D:/Documents/Dropbox/Implicit Mindset Measure/Data/Raw/Temp/neptun_duplicate_joined.csv")
#write_csv2(neptun_duplicate_time1, "D:/Documents/Dropbox/Implicit Mindset Measure/Data/Temp/neptun_duplicate_time1.csv")
#write_csv2(neptun_duplicate_time2, "D:/Documents/Dropbox/Implicit Mindset Measure/Data/Temp/neptun_duplicate_time2.csv")
```



##Counting number of participants in groups
```{r}
joined$group <- ifelse(joined$TIME_between_end > 20, 1, 0)

joined %>% 
  count(group)
```

##Plotting frequency of number of days between data collections
```{r}
joined$TIME_between_end <- as.numeric(joined$TIME_between_end)
plot <- ggplot(joined, aes(TIME_between_end))
plot + geom_bar()
```
#Analysis

##Importing data
```{r}

```

